An Example Article using \aastex v6.2\footnote{Released on January, 8th, 2018}

### 2018-02-10 paper/ms.tex
move paper to aas template

\documentclass{article}
\usepackage{amsmath, amssymb, mathtools, bm}
\usepackage{graphicx, graphics}
\usepackage{array}
\usepackage{geometry}
\geometry{lmargin=3cm, tmargin=3cm, bmargin=2cm, rmargin=2cm}
\DeclareMathOperator*{\argmin}{arg\,min}

\title{\texttt{lightkurve}: Open source Python data analysis for NASA's Kepler, K2, and TESS missions}
\author{\texttt{lightkurve} and PyKE Contributors}
\date{\today}

\begin{document}
\maketitle

@@

@@

\section{Introduction}

\section{Lightcurve Basics}
    \subsection{The \texttt{LightCurve} class}
        A \texttt{LightCurve} object can be instantiated by passing a \texttt{time}
        array, a \texttt{flux} array, and optionally a \texttt{flux\_err} array which
        accounts for uncertainties in the \texttt{flux} measurements, i.e.,
        \begin{verbatim}
        from lightkurve.lightcurve import LightCurve
        lc = LightCurve(time, flux)
        \end{verbatim}

        The \texttt{LightCurve} object provides methods described in
        Table~(\ref{tab:methods}).

        \begin{table}[!htb]
            \centering
            \caption{A subset of methods provided by the \texttt{LightCurve} class}
            \begin{tabular}{cp{12cm}}
                \hline
                \textbf{Method signature} & \textbf{Short description} \\
                \hline
                \texttt{stitch} & appends the attributes \texttt{flux},
                \texttt{time}, and \texttt{flux\_err} of other given
                \texttt{LighCurve} objects.\\
                \texttt{flatten} & applies a Savitzky-Golay filter to capture
                low frequency flux variations which can be then removed in order
                to aid transit detection algorithms.\\
                \texttt{fold} & folds a lightcurve at a given period and phase.\\
                \texttt{bin} &  bins a lightcurve using a block mean or median.\\
                \texttt{cdpp} &  computes the Combined Differential Photometric
                Precision (CDPP) metric, which is a proxy for the amount of
                scatter in the lightcurve signal. \\
                \texttt{plot} & displays a lightcurve.
            \end{tabular}
            \label{tab:methods}
        \end{table}

       The \texttt{KeplerLightCurve} class extends \texttt{LightCurve} by
       adding attributes to store metadata information such as channel number,
       quality flags, campaign or quarter number, kepler id, etc.

@@

        Therefore, one can, for example, perform the following series of operations
        in order to fold a lightcurve from the MAST archive
\begin{verbatim}
>>> lc_file = KeplerLightCurveFile("https://archive.stsci.edu/missions/kepler/"
... "lightcurves/0119/011904151/kplr011904151-2009350155506_llc.fits")
>>> klc = lc_file.get_lightcurve("PDCSAP_FLUX").fold(period=0.837495)
>>> klc.plot()
\end{verbatim}
        \begin{figure}[!htb]
            \centering
            \includegraphics[scale=.5]{figs/fold-lc.pdf}
            \caption{Folded lightcurve of target \texttt{KIC011904151} quarter 3, showing the
            transit signal of Kepler-10b.}
            \label{fig:fold-method}
        \end{figure}

@@

\begin{figure}[!htb]
    \centering
    \includegraphics[scale=.4]{figs/tpf-plot.pdf}
    \includegraphics[scale=.4]{figs/tpf-plot-aperture.pdf}
    \caption{Displaying a given frame of a TPF using \texttt{plot}.
    Optionally, an \texttt{aperture\_mask} can be passed which is
    highlighted on the right hand side.}
    \label{fig:plot-method}
\end{figure}

@@

Cotrending basis vectors (CBVs) can remove global correlated
systematics present in a given channel \cite{2012PASP..124.1000S}.

@@

However,~(\ref{eq:chi-square} is known to be sensitive to outliers [add reference],
therefore, as a default behaviour in \texttt{lightkurve}, we use the following cost
function
\begin{align}
    \mathcal{C}(\bm{\theta}, f_SAP) = \sum_{t} \left\rvert f_{SAP}(t)
    - \sum_{j=1}^{n}\theta_j v_{j}(t)\right\rvert,
\label{eq:l1-norm}
\end{align}

@@

Fig~\ref{fig:cbv-correction} illustrates the correction.

\begin{figure}[!htb]
    \centering
    \includegraphics[scale=.5]{figs/cbv.pdf}
    \caption{CBV correction applied on \texttt{KOI 8462852}}
    \label{fig:cbv-correction}
\end{figure}

\cite{2014sdmm.book.....I}.

@@

In the same fashion, we can apply cotrending basis vector correction to
$\mathcal{K}\mathit{2}$ lightcurves.

Fig.~\ref{fig:cbv-correction-k2} shows the detrended lightcurve after estimating
the first nine coefficients for CBV correciton on $\mathcal{K}\mathit{2}$ target
 \texttt{EPIC 201543306}. The selection of the number of CBVs is set by inspecting the
grid search curve can be set through model comparison heuristics like AIC, BIC,
or cross-validation \cite{2014sdmm.book.....I}.

\begin{figure}[!htb]
    \centering
    \includegraphics[scale=.5]{figs/cbv-k2.pdf}
    \caption{CBV correction applied on \texttt{EPIC 201543306}.}
    \label{fig:cbv-correction-k2}
\end{figure}

@@

\begin{figure}[!htb]
    \centering
    \includegraphics[scale=.5]{figs/cbv-grid-search.pdf}
    \caption{Grid search on the number of CBVs}
    \label{fig:cbv-grid-search}
\end{figure}

% MGS note: Wait--- won't the cost function decrease monotonically for CBVs?
% Do you use AIC or BIC or cross-validation?
An objective way of selecting the number of CBVs is to use Bayes' factors
[add reference]. In the Bayes' factor setting, the selected number of
CBVs is the one that provide the least gain in posterior probability, i.e.,
for all ordered pairs of CBVs, the Bayes factor selects $n^{*}$ number of CBVs
as follows
\begin{align}
    n^{*} = \argmin_{n} $\dfrac{p_{n+1}}{p_n}$,
\end{align}
in which $p_n$ is the posterior probability evaluated at the Maximum A Posteriori
Estimator (MAP) obtained using $n$ CBVs.

@@

\begin{figure}[!htb]
    \centering
    \includegraphics[scale=.5]{figs/cbv-bayes-factor.pdf}
    \caption{Bayes factors as a function of the number of CBVs for \texttt{EPIC 201543306}}
    \label{fig:cbv-grid-search}
\end{figure}

@@

lightkurve contains routines to perform PSF photometry in TPFs
which are implemented in the \texttt{psf} module.

@@

@@

From a probabilistic point of view, one is often interested in minimizing the
expected cost with respect to some probability distribution assigned to the data
$\bm{y}$ and to the parameter vector $\bm{\theta}$, from which the cost function
$R$ naturally arises. The default assumption on the data is that it follows
a Poisson probability distribution; whereas the probability distribution on the
parameter vector has to be assigned by the user using the $\texttt{prior}$
argument.

@@

\subsection{Motion-dependent Correlated Noise}

Spacecraft-induced correlated noise remains one of the greatest hurdles to analyzing K2 lightcurves.  Many algorithms have been developed to mitigate motion-dependent artifacts \cite{vanderburg14}.  Local and global Gaussian Process covariance kernels...

\label{subsection:motion}

\section{Acknowledgments}
lightkurve is build on top of numerous packages that constitute the Scientific Python
stack, more precisely, \texttt{numpy}, \texttt{scipy}, \texttt{matplotlib}, and
\texttt{astropy}.

\clearpage

%% MGS 2/2018: Uncomment below to enable references.
%\bibliographystyle{aasjournal}
%\bibliography{ms}

>>>>

%%
%% Beginning of file 'sample62.tex'
%%
%% Modified 2018 January
%%
%% This is a sample manuscript marked up using the
%% AASTeX v6.2 LaTeX 2e macros.
%%
%% AASTeX is now based on Alexey Vikhlinin's emulateapj.cls 
%% (Copyright 2000-2015).  See the classfile for details.

%% AASTeX requires revtex4-1.cls (http://publish.aps.org/revtex4/) and
%% other external packages (latexsym, graphicx, amssymb, longtable, and epsf).
%% All of these external packages should already be present in the modern TeX 
%% distributions.  If not they can also be obtained at www.ctan.org.

%% The first piece of markup in an AASTeX v6.x document is the \documentclass
%% command. LaTeX will ignore any data that comes before this command. The 
%% documentclass can take an optional argument to modify the output style.
%% The command below calls the preprint style  which will produce a tightly 
%% typeset, one-column, single-spaced document.  It is the default and thus
%% does not need to be explicitly stated.
%%
%%
%% using aastex version 6.2
\documentclass[twocolumn]{aastex62}
\usepackage{amsmath, amssymb, mathtools, bm}

\newcommand{\KTWO}{$\mathcal{K}\mathit{2}$}
\newcommand{\lightkurve}{\texttt{lightkurve}}
\newcommand{\LightCurve}{\texttt{LightCurve}}
\newcommand{\KeplerLightCurve}{\texttt{KeplerLightCurve}}
\newcommand{\numpy}{\texttt{numpy}}

\DeclareMathOperator*{\argmin}{arg\,min}

\newcommand{\vdag}{(v)^\dagger}
\newcommand\aastex{AAS\TeX}
\newcommand\latex{La\TeX}

%% Reintroduced the \received and \accepted commands from AASTeX v5.2
\received{January 1, 2018}
\revised{January 7, 2018}
\accepted{\today}
%% Command to document which AAS Journal the manuscript was submitted to.
%% Adds "Submitted to " the arguement.
\submitjournal{ApJ}

%\shorttitle{Sample article}
%\shortauthors{Schwarz et al.}

\begin{document}

\title{An Example Article using \aastex v6.2\footnote{Released on January, 8th, 2018}}

\correspondingauthor{Geert Barentsen}
\email{hello@geert.io}

\author{\lightkurve contributors}
\affil{The galatic startup}

\author{August Muench}
\affiliation{American Astronomical Society \\
2000 Florida Ave., NW, Suite 300 \\
Washington, DC 20009-1231, USA}
\collaboration{(AAS Journals Data Scientists collaboration)}

@@

    This paper presents an open source package for NASA's Kepler, \KTWO, and
    TESS.

@@

%% Keywords should appear after the \end{abstract} command. 
%% See the online documentation for the full list of available subject
%% keywords and the rules for their use.
\keywords{editorials, notices ---
miscellaneous --- catalogs --- surveys}

\section{Introduction} \label{sec:intro}
NASA's Kepler and \KTWO~missions have been delivering high-precision time
series data for a wide range of stellar types.

\section{Lightcurve Basics}

\subsection{The \LightCurve~and \KeplerLightCurve~class}
        The \LightCurve~class is a simple cointainer to store \numpy~arrays
        (hereafter, arrays) related to flux time-domain measurements.

        The \LightCurve~object provides methods to store, process, and
        convert lightcurves. Table~\ref{tab:methods} contains a description
        of a subset of the methods.

        \begin{table}[!htb]
            \centering
            \caption{A subset of methods provided by the \LightCurve~class}
            \begin{tabular}{cp{5cm}}
                \hline
                \textbf{Method signature} & \textbf{Short description} \\
                \hline
                \texttt{stitch} & appends the attributes \texttt{flux},
                \texttt{time}, and \texttt{flux\_err} of other given
                \texttt{LighCurve} objects.\\
                \texttt{flatten} & applies a Savitzky-Golay filter to capture
                low frequency flux variations which can be then removed in order
                to aid transit detection algorithms.\\
                \texttt{fold} & folds a lightcurve at a given period and phase.\\
                \texttt{bin} &  bins a lightcurve using a block mean or median.\\
                \texttt{cdpp} &  computes the Combined Differential Photometric
                Precision (CDPP) metric, which is a proxy for the amount of
                scatter in the lightcurve signal. \\
                \texttt{plot} & displays a lightcurve.
            \end{tabular}
            \label{tab:methods}
        \end{table}

        A \LightCurve
        object can be instantiated by passing a \texttt{time} array, a
        \texttt{flux} array, and, optionally, a \texttt{flux\_err} array
        which accounts for uncertainties in the \texttt{flux} measurements, i.e.,
        \begin{verbatim}
        >>> from lightkurve import LightCurve
        >>> lc = LightCurve(time, flux)
        \end{verbatim}

       The \KeplerLightCurve class extends \LightCurve by
       adding attributes to store metadata information such as channel number,
       quality flags, campaign or quarter number, kepler id, etc.

@@

        Therefore, one can, for example, perform the following series of operations
        in order to fold a lightcurve from the MAST archive
\begin{verbatim}
>>> lc_file = KeplerLightCurveFile("https://archive.stsci.edu/missions/kepler/"
... "lightcurves/0119/011904151/kplr011904151-2009350155506_llc.fits")
>>> klc = lc_file.get_lightcurve("PDCSAP_FLUX").fold(period=0.837495)
>>> klc.plot()
\end{verbatim}

\begin{figure}
\plotone{figs/fold-lc.pdf}
\caption{Folded lightcurve of target \texttt{KIC011904151} quarter 3, showing the
            transit signal of Kepler-10b.
\label{fig:fold-method}}
\end{figure}

@@

\begin{figure}[!htb]
    \centering
    \plotone{figs/tpf-plot.pdf}
    \plotone{figs/tpf-plot-aperture.pdf}
    \caption{Displaying a given frame of a TPF using \texttt{plot}.
    Optionally, an \texttt{aperture\_mask} can be passed which is
    highlighted on the right hand side.}
    \label{fig:plot-method}
\end{figure}

In an image with $n$ pixels, where the flux and the center positions of the
$i$-th pixel are denoted as $f_i$ and $(x_i, y_i)$, respectively, the centroids
may be expressed as
\begin{align}
    x^{\star} = \dfrac{\sum_{i=1}^{n} f_i x_i}{\sum_{i=1}^{n}f_i} \\
    y^{\star} = \dfrac{\sum_{i=1}^{n} f_i y_i}{\sum_{i=1}^{n}f_i}.
\end{align}

In \texttt{lightkurve}, the centroids in every cadence can be computed as
\begin{verbatim}
>>> from lightkurve import KeplerTargetPixelFile
>>> tpf = KeplerTargetPixelFile('ktwo246199087-c12_lpd-targ.fits.gz')
>>> x_star, y_star = tpf.get_centroids()
\end{verbatim}

@@

Cotrending basis vectors (CBVs) can remove global correlated
systematics present in a given channel \cite{smith2012}.

@@

However, Equation~(\ref{eq:chi-square}) is sensitive to outliers~\cite{ivezi2014},
therefore, as a default behaviour in \lightkurve, we use the following cost
function
\begin{align}
    \mathcal{C}(\bm{\theta}, f_SAP) = \sum_{t} \left\rvert f_{SAP}(t)
    - \sum_{j=1}^{n}\theta_j v_{j}(t)\right\rvert.
\label{eq:l1-norm}
\end{align}

@@

Fig~\ref{fig:cbv-correction} illustrates the correction. The pink line has a shift from
the green line because in \lightkurve~we do not account the flux lost outside of the aperture mask.

\begin{figure}[!htb]
    \centering
    \plotone{figs/cbv.pdf}
    \caption{CBV correction applied on \texttt{KOI 8462852}}
    \label{fig:cbv-correction}
\end{figure}

@@

In the same fashion, we can apply cotrending basis vector correction to
\KTWO lightcurves.

Fig.~\ref{fig:cbv-correction-k2} shows the detrended lightcurve after estimating
the first nine coefficients for CBV correciton on \KTWO target
 \texttt{EPIC 201543306}. The selection of the number of CBVs is set by inspecting the
grid search curve can be set through model comparison heuristics like AIC, BIC,
or cross-validation \cite{ivezi2014}.

\begin{figure}
    \centering
    \plotone{figs/cbv-k2.pdf}
    \caption{CBV correction applied on \texttt{EPIC 201543306}.
    \label{fig:cbv-correction-k2}}
\end{figure}

@@

\begin{figure}[!htb]
    \centering
    \plotone{figs/cbv-grid-search.pdf}
    \caption{Grid search on the number of CBVs}
    \label{fig:cbv-grid-search}
\end{figure}

% MGS note: Wait--- won't the cost function decrease monotonically for CBVs?
% Do you use AIC or BIC or cross-validation?
An objective way of selecting the number of CBVs is to use Bayes' factors
[add reference]. In the Bayes' factor setting, the selected number of
CBVs is the one that provide the least gain in posterior probability, i.e.,
for all ordered pairs of CBVs, the Bayes factor selects $n^{*}$ number of CBVs
as follows
\begin{align}
    n^{*} = \argmin_{n} \dfrac{p_{n+1}}{p_n},
\end{align}
in which $p_n$ is the posterior probability evaluated at the Maximum A Posteriori
Estimator (MAP) obtained using $n$ CBVs.

@@

\begin{figure}[!htb]
    \centering
    \plotone{figs/cbv-bayes-factor.pdf}
    \caption{Bayes factors as a function of the number of CBVs for \texttt{EPIC 201543306}}
    \label{fig:cbv-grid-search}
\end{figure}

@@

\lightkurve ~contains routines to perform PSF photometry in TPFs
which are implemented in the \texttt{psf} module.

@@

From a probabilistic point of view, one is often interested in minimizing the
expected cost with respect to some probability distribution assigned to the data
$\bm{y}$ and to the parameter vector $\bm{\theta}$, from which the cost function
$R$ naturally arises. The default assumption on the data is that it follows
a Poisson probability distribution, whereas the probability distribution on the
parameter vector has to be assigned by the user using the $\texttt{prior}$
argument. Using a uniform prior for $\bm{\theta}$, the MAP estimator can be written
as
\begin{align}
    \bm{\theta}^{*}(\bm{y}) = \argmin_{\bm{\theta} \in \Lambda} \sum_{i=1}^{n}
    \left(\sum_{j=1}^{m}\lambda_i(\bm{\theta}_j) - y_i\log\sum_{j=1}^{m}\lambda_i(\bm{\theta}_j)\right),
\end{align}
in which $\Lambda$ is the support of $\bm{\theta}$.

@@

@@

\subsection{Motion-dependent Correlated Noise}
\label{subsection:motion}

Spacecraft-induced correlated noise remains one of the greatest hurdles to
analyzing K2 lightcurves. Many algorithms have been developed to mitigate
motion-dependent artifacts~\cite{vanderburg14}.

%% If you wish to include an acknowledgments section in your paper,
%% separate it off from the body of the text using the \acknowledgments
%% command.
\acknowledgments

We thank all the people that have made this AASTeX what it is today.  This
includes but not limited to Bob Hanisch, Chris Biemesderfer, Lee Brotzman,
Pierre Landau, Arthur Ogawa, Maxim Markevitch, Alexey Vikhlinin and Amy
Hendrickson. Also special thanks to David Hogg and Daniel Foreman-Mackey
for the new "modern" style design. Considerable help was provided via bug
reports and hacks from numerous people including Patricio Cubillos, Alex
Drlica-Wagner, Sean Lake, Michele Bannister, Peter Williams, and Jonathan
Gagne.

\vspace{5mm}
\facilities{HST(STIS), Swift(XRT and UVOT), AAVSO, CTIO:1.3m,
CTIO:1.5m,CXO}

\software{astropy}

%% Appendix material should be preceded with a single \appendix command.
%% There should be a \section command for each appendix. Mark appendix
%% subsections with the same markup you use in the main body of the paper.

%% Each Appendix (indicated with \section) will be lettered A, B, C, etc.
%% The equation counter will reset when it encounters the \appendix
%% command and will number appendix equations (A1), (A2), etc. The
%% Figure and Table counter will not reset.

\appendix

\section{Appendix information}

\bibliographystyle{aasjournals}
\bibliography{ms}
